A Domain Specific Language for SpectreGuard

### 2020-12-07 paper/main.tex
More on sensitivity types. Foreshadow analysis section

\section{Sensitivity Types}
The Haskell type system is leveraged to perform a basic static consistency check of the sensitivities
of variables, so that a variable does not get assigned to a variable of a different sensitivity. This
is done by making the \verb|Expr| type constructor take a phantom type argument~\cite{Phantom}. The
logical inference rules corresponding to this check are given in Fig. \ref{fig:SensTypes}. An introduction
to this style of inference rule system, with many examples and applications in the study of programming languages, is given in \cite{HarperFoundations}.

@@

A typing judgement is expressed with the syntax

@@

where \ttt{x} is some expression or command in the EDSL. This judgement means
that \ttt{x} has type $\beta$. This is also the same syntax used by Haskell, and by extension
the EDSL, to explicitly specify the type of any expression when necessary or desired.

>>>>

\section{Sensitivity Types}
The Haskell type system is leveraged to perform a basic static consistency check
of the sensitivities of variables, so that a variable does not get assigned to a
variable of a different sensitivity. This is done by making the \verb|Expr| type
constructor take a phantom type argument~\cite{Phantom}. The phantom type
argument is the \textit{sensitivity type} of that expression.  The logical
inference rules corresponding to this check are given in Fig.
\ref{fig:SensTypes}. Note that the EDSL inherits the rest of Haskell's type
system in addition to these rules. Only the aspects of the type system that is
particularly relevant to the EDSL is reflected in the figure, often specialized
to the particular scenario encountered in using sensitivity types in the EDSL.
An introduction to this style of inference rule system, with many examples and
applications in the study of programming languages, is given in
\cite{HarperFoundations}.

Observe that an two expressions with different sensitivity types cannot be
combined into a larger compound expression. However, commands (represented by
the \verb|Cmd| type constructor) often have expressions embedded in them and
commands can be sequenced with each other.  There is no restriction on how two
commands can be combined, even if they involve expressions with different
sensitivity types. This freedom in combining commands independently of
sensitivity foreshadows the essence of the problem we will encounter in
Section \ref{sec:Analysis}. For now, note that all control flow constructs are
part of the command type (as opposed to the expression type).

@@

\noindent A typing judgement is expressed with the syntax

@@

\noindent where \ttt{x} is some expression or command in the EDSL. This judgement means
that \ttt{x} has type $\beta$. This is also the same syntax used by Haskell, and by extension
the EDSL, to explicitly specify the type of any expression when necessary or desired.
